\myfont Implementation and evaluation of register allocation used to translate LLVM-{}- to x86-64

### 2024-01-07 article.tex
Begin coalescing

Since all edges are preserved, the resulting node \(ab\) may be of a much higher degree. Because of this, only strategies that produce a \(k\)-colorable graph are worth considering, as additional spills negate the purpose entirely.

>>>>

Since all edges are preserved, the resulting node \(ab\) may be of a much higher degree. Because of this, only strategies that produce a \(k\)-colorable graph are worth considering, as additional spills negate the purpose entirely. One of the  strategies introduced in the Appel text is the \textit{Briggs} strategy  \cite[232]{tiger}, in which nodes \(a\) and \(n\) can be coalesced if and only if the resulting node \(ab\) is of insignificant degree  (i.e. \(\leq K\)).

The strategy Since the only move operations in use in LLVM-{}- are phi nodes,
